### 2010-06-14 code/subarchitectures/visualization.sa/trunk/doc/v11n.tex
v11n: cmakelists - new options

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
   option(BUILD_SA_VISUALIZATION "Build visualization libraries (Requires QT4)" NO)
   if(BUILD_SA_VISUALIZATION)
      set(VISUALIZATION_INCLUDE_DIRS
         ${COGX_ROOT}/subarchitectures/visualization.sa/src/c++/autogen
         ${COGX_ROOT}/subarchitectures/visualization.sa/src/c++/core
         )
      set(VISUALIZATION_LIBRARIES
         DisplayClient VisualizationData
         )
      add_subdirectory(subarchitectures/visualization.sa)
      add_definitions(-DFEAT_VISUALIZATION)
   endif(BUILD_SA_VISUALIZATION)
\end{Verbatim}

Finally run \code{ccmake} and set \code{BUILD\_VISUALIZATION\_SA} to \code{ON}
to enable the visualization subarchitecture.

@@

The library provides a display server that displays objects created by its
clients.  The objects that are on the display server are grouped into views.
Initially every new object is displayed in its own view that has the same name
as the object.
\todo{(TODO: Additional views that display multiple objects can be defined on the server)}
The display server creates rendering contexts in which the views are displayed.
There are three types of contexts: 2D, OpenGL and HTML.
% (TODO: new contexts: tabular; textual; ...)

>>>>

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
   option(BUILD_SA_V11N "Build visualization libraries (Requires QT4)" NO)
   if(BUILD_SA_V11N)
      set(VISUALIZATION_INCLUDE_DIRS
         ${COGX_ROOT}/subarchitectures/visualization.sa/src/c++/autogen
         ${COGX_ROOT}/subarchitectures/visualization.sa/src/c++/core
         )
      set(VISUALIZATION_LIBRARIES
         DisplayClient VisualizationData
         )
      add_subdirectory(subarchitectures/visualization.sa)
      add_definitions(-DFEAT_VISUALIZATION)
   endif(BUILD_SA_V11N)
\end{Verbatim}

Finally run \code{ccmake} and set \code{BUILD\_SA\_V11N} to \code{ON} to enable
the visualization subarchitecture.

@@

The library provides a display server that displays objects created by its
clients.  The objects that are on the display server are grouped into views.
Initially every new object is displayed in its own view that has the same name
as the object.
\todo{(TODO: It will be posible to define additional views that display multiple objects)}
The display server creates rendering contexts in which the views are displayed.
There are three types of contexts: 2D, OpenGL and HTML.
% (TODO: additional contexts: eg. tabular)
